\LARGE \bf On the use of vehicle categorization and context information for messages forwarding in VANETs

### 2016-09-17 paperITSC.tex
USING ONTOLOGY FOR VEHICLES CATEGORIZATION test

Ontology is an organized form of representing the data. It is use to represent different kinds of objects and show relationship among them. It provides a common vocabulary to enable interoperability, resolve ambiguity and hence to describe concepts and the relations that exist between them \cite{madkour2011}.

A single ontology for an area is not sufficient, as it can grow fast and will require increasing amount of resources to host, manage, and use. Hence, there is a need for more than one ontology. In case of more than one ontology, they are classified according to the level of detailed knowledge they provide \cite{packer2010}. Consequently, we have more than one ontologies for the vehicular scenarios (e.g., for sales, used cars, manufacture).

Ontology for context information can be use as a formal context model that allows an efficient gathering, managing and storing of the context information. Likewise, it provides interoperability in heterogeneous systems, by defining a common set of concepts about context while interacting. It also enables reasoning mechanisms to infer high-level information from a raw context, find and solve inconsistencies. Additionally, it facilitates the reuse of the knowledge \cite{serrano2007}.

For our work, we used the ontology\footnote{Draft available on (http://auto.sdo-gao.appspot.com/) Access in: 14 June 2016} proposed in \cite{gao_2016} that categorizes the vehicle according to its physical features (e.g., size of vehicle, number of axis) to represent the vehicles categories. Furthermore, we also need to categorize the vehicles by its usage (i.e., private car, taxi). Therefore, we have added in the ``\emph{CarUsageType}'' a vehicle usage category. This category defines how the vehicle will be used and allows the extraction of mobility patterns information. The physical category should be used by traffic management companies, for instance, in the toll collection. While, the usage category can be used by forwarding protocols to decide which node is the best to carry a message. In our protocol, the vehicle usage category information are send by vehicles, along with other information collected from sensors.

>>>>

Ontology is an organized form of representing the data. It is used to represent different kinds of objects and show the relationship among them. It provides a common vocabulary to enable interoperability, resolve ambiguity and hence to describe concepts and the relations that exist between them \cite{madkour2011}.

A single ontology for an area is not sufficient, as it can grow fast and will require increasing amount of resources to host, manage, and use. Hence, there is a need for more than one ontology. In the case of more than one ontology, they are classified according to the level of detailed knowledge they provide \cite{packer2010}. Consequently, we have more than one ontologies for the vehicular scenarios (e.g., for sales, used cars, manufacture).

Ontology for context information can be use as a formal context model that allows an efficient gathering, managing and storing the context information. Likewise, it provides interoperability in heterogeneous systems, by defining a common set of concepts about context while interacting. It also enables reasoning mechanisms to infer high-level information from a raw context, find and solve inconsistencies. Additionally, it facilitates the reuse of the knowledge \cite{serrano2007}.

For our work, we used the ontology\footnote{Draft available on (http://auto.sdo-gao.appspot.com/) Access in: 14 June 2016} proposed in \cite{gao_2016} that categorizes the vehicle according to its physical features (e.g., size of the vehicle, the number of axes) to represent the vehicles categories. Furthermore, we also need to categorize the vehicles by its usage (i.e., private car, taxi). Therefore, we have added in the ``\emph{CarUsageType}'' a vehicle usage category. This category defines how the vehicle will be used and allows the extraction of mobility patterns information. The physical category should be used by traffic management companies, for instance, in the toll collection. While, the usage category can be used by forwarding protocols to decide which node is the best to carry a message. In our protocol, the vehicle usage category information is sent by vehicles, along with other information collected from sensors.
